\section{Requirements}
\subsection{Problem Statement}
\begin{center}
    \textbf{``Design and Manufacture a machine to clean manufacturing stains off an unbleached cotton cloth ''}
\end{center}

\subsection{Input Requirements}
\subsubsection{Cloth Details}
\begin{itemize}
    \item[$\scriptstyle\circ$] The cloth being cleaned is just-manufactured, uncolored cotton cloth, for general usage. The thickness is 1-ply, with a \gls{thread count} of 400, and of \gls{denier} 60 \gls{opaqueness}.
    \item[$\scriptstyle\circ$] The dimensions of the cloth to be cleaned are a maximum of \SI{10}{\meter} length and 2m width or a continuous roll of \SI{2}{\meter} width.
    \item[$\scriptstyle\circ$] The cloth, if uncut, needs to be cut to \SI{10}{\meter}$\times$\SI{2}{\meter} in size.
    \item[$\scriptstyle\circ$] The cloth has mostly oil-based stains, to begin with, naturally imbued during the manufacturing process.
\end{itemize}
\subsubsection{Other inputs}
\begin{itemize}
    \item[$\scriptstyle\circ$] The machine works with pressured water available at an ambient temperature from a \SI{35}{\meter} overhead tank of capacity \SI{50}{\liter} on-site. 
    \item[$\scriptstyle\circ$] The machine works with water of $\SI{80}{\milli\gram\per\liter}$ $CaCO_3$ equivalent \gls{hardness}.
    \item[$\scriptstyle\circ$] \gls{Expendable materials} like detergents, soaps, etc are to be treated as a running cost, and paid for by the client after installation.
\end{itemize}
\subsubsection{Mode of Input}
\begin{itemize}
    \item[$\scriptstyle\circ$] The machine cleans in batches of \SI{11}{\kilogram} dry weight per batch.
    \item[$\scriptstyle\circ$] Only a single program for general washing is required.
    \item[$\scriptstyle\circ$]The machine is required to have the capability to sequentially process multiple batches prepared beforehand by the client. 
\end{itemize}

\subsection{Output Requirements}
\begin{itemize}
    \item[$\scriptstyle\circ$] The machine is required to both wash and dry the cloth. 
    \item [$\scriptstyle\circ$] The \SI{10}{\meter} x \SI{2}{\meter} output cloth needs to be rolled.
    \item [$\scriptstyle\circ$] The output should be bone-dry.
\end{itemize}
\subsection{Power Requirements}
\begin{itemize}
    \item[$\scriptstyle\circ$] The machine must be compatible with \SI{220}{\volt} AC 1-$\Phi$ (desirable) and \SI{440}{\volt} AC 3-$\Phi$ power drawing a maximum current of \SI{15}{\ampere}.
    \item[$\scriptstyle\circ$] The machine must be able to be connected to plug points up to \SI{20}{\meter} away. 
\end{itemize}
%\subsection{Logistical Requirements}
\subsection{Environmental Requirements}
\begin{itemize}
    \item[$\scriptstyle\circ$] The machine must use as low an amount of resources(water, electricity) as possible, and comply with \Gls{CPCB Regulations}. 
\end{itemize}
\subsection{Site-Demanded Requirements}
\begin{itemize}
    \item[$\scriptstyle\circ$] The machine is designed to be used at \gls{semi-industrial sites}. 
    \item[$\scriptstyle\circ$] During its operation, the machine must not exceed a noise level of \SI{70}{\decibel}. 
    \item[$\scriptstyle\circ$] The machine is desired to be disassembleable and re-installable on request. 
\end{itemize}
\subsection{Structural Requirements}
\begin{itemize}
    \item[$\scriptstyle\circ$] The machine must be of maximum dimensions \SI{25}{\meter}$\times$\SI{40}{\meter}$\times$\SI{60}{\meter}, designed to be installed in an industrial-size enclosure, or an open courtyard. 
\end{itemize}
\subsection{Time Requirements}
\subsubsection{Operational Time}
    \begin{itemize}
        \item[$\scriptstyle\circ$] The maximum time to wash and dry a batch must be under 45 minutes. 
    \end{itemize}
%\subsubsection{Time to Market Requirements}
%\subsubsection{Life Time Requirements}
%\subsubsection{End of Life Requirements}
% \subsection{Miscellaneous Requirements}